Association between Breast Cancer and Hepatitis C Virus with Age Controlling

### 2022-11-15 manuscript/manuscript.tex
equations

To test the association of breast cancer and Hepatitis C seropositivity, one can use
the chi-square or Fisher's Exact test, depending on the
conditions from the sample size \citep{warner2013testing}. Fisher's
exact test is useful for when the normality assumption is violated 
and the expected values of the 2x2 table are too small. The test uses 
the hypergeometric distribution to test if the probabilities are
the same between the two groups. Thus, we can determine if there is 
more of a risk of breast cancer for those with seropositive Hep C.
In the data section, the data was summarized into 2x2 contingency tables.
The generalzied table is shown in Figure~\ref{fig:table}.
The first step is calculate the probability of the original table occuring,
using the hypergeometric pdf. Figure~\ref{fig:formula} shows the formula used.

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width=8cm]{formula.png}
  \caption{Hypergeometric pmf}
  \label{fig:formula}
\end{figure}

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width=8cm]{breslow day test stat.png}
  \caption{Breslow Day Test Statistic}
  \label{fig:BD}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[width=8cm]{MH Test Stat.png}
  \caption{Mantel-Haenszel Test Statistic}
  \label{fig:MH}
\end{figure}

After calculating the crude estimate, a Breslow-Day test will test for 
homogeneity of odds ratios between the age stratified data. The generalized
form of stratified 2x2 contingency tables is shown in Figure~\ref{fig:strat}.
The Breslow-Day test statistic is shown in Figure~\ref{fig:BD}, which will
be computed using SAS.

Based on the results of the Breslow Day test for homogeneity of odds ratios,
the Mantel-Haenszel test will compute a common odds ratio and test if there 
is an association between seropositivity and breast cancer while controlling 
for age. The Mantel-Haenszel test statistic is shown in Figure~\ref{fig:MH}
where the expected value of A is 
\begin{equation}
  E(A_{i})=\frac{M_{i1}R_{1i}}{N_{i}} 
\end{equation}
and the variance of A is 
\begin{equation}
  V(A_{i})=\frac{R_{1i}R_{0i}M_{1i}M_{0i}}{N_i^2(N_{i}-1)}. 
\end{equation}

@@

\section{Discussion}
\label{sec:discuss}
Based on the

>>>>

To test the association of breast cancer and Hepatitis C seropositivity, one can use
the chi-square or Fisher's Exact test, depending on the
conditions from the sample size \citep{warner2013testing}. Fisher's
exact test is useful for when the normality assumption is violated 
and the expected values of the 2x2 table are too small. The test uses 
the hypergeometric distribution to test if the probabilities are
the same between the two groups. Thus, we can determine if there is 
more of a risk of breast cancer for those with seropositive Hep C.
In the data section, the data was summarized into 2x2 contingency tables.
The generalzied table is shown in Figure~\ref{fig:table}.
The first step is calculate the probability of the original table occuring,
using the hypergeometric pdf:
\begin{equation}
P_a=[\frac{(a+b+c+d)a!b!c!d!}{(a+c)!(b+d)!(a+b)!(c+d)!}]^-1
\end{equation}

@@

@@

After calculating the crude estimate, a Breslow-Day test will test for 
homogeneity of odds ratios between the age stratified data. The generalized
form of stratified 2x2 contingency tables is shown in Figure~\ref{fig:strat}.
The Breslow-Day test statistic will be computed using SAS with the formula:
\begin{equation}
  \chi_{BD}^2=\displaystyle\sum\limits_{i=0}^s\frac{[A_i-E(A_i|\hat{OR}_{M-H})]^2}{Var(A_i|\hat{OR}_{M-H})}
\end{equation}

Based on the results of the Breslow Day test for homogeneity of odds ratios,
the Mantel-Haenszel test will compute a common odds ratio and test if there 
is an association between seropositivity and breast cancer while controlling 
for age. The Mantel-Haenszel test statistic is:
\begin{equation}
  \chi_{M-H}^2=\frac{(|\sum\limits_{i=0}^s A_i - \sum\limits_{i=0}^sE(A_i)|-0.5)^2}
{\sum\limits_{i=0}^s V(A_i)}
\end{equation}

The expected value and variance of A for the ith strata is 
\[
  E(A_{i})=\frac{M_{i1}R_{1i}}{N_{i}} 
\]
\[
  V(A_{i})=\frac{R_{1i}R_{0i}M_{1i}M_{0i}}{N_i^2(N_{i}-1)}. 
\]

@@

\section{Discussion}
\label{sec:discuss}
Based on the analysis, it is evident that for women under the age of 45,
seropositivity and breast cancer are strongly associated. As being HCV 
positive can complicate treatment of cancer, this is critical information.
In Egypt, breast cancer remains the most common form or cancer and high 
levels of hepatitus C continue. This study was retrospective so analysis 
was limited to observing odds ratios and the sample size was quite small.
Thus, future studies should aim to be prospective cohort studies so 
researchers can observe how seropisitivity and breast cancer interact 
over time. 
Additionally, age is just one factor that can affect the associaiton 
between hepatitus C and breast cancer. Future studies should dive 
deeper into more factors such as weight, reproductive history, 
and alcohol consumption. Addiitonally, future studies can explore how 
seropositivity affects tumor size, disease agression, and more. As 
breast cancer is so prevalent in Egypt, further understanding the 
risk factors is becoming even more importnant.
